### 2019-12-05 RFCs/HDF5/VOL/connector_author_guide/connector_interface.tex
Extra pass over GET/SPECIFIC callback variable args.
Former-commit-id: aa84c8f75e1afd60adf7115cbb8e8fc08ae5db08

\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
  \texttt{attr} & (IN): An attribute or location object where information
  needs to be retrieved from.\\
  \texttt{get\_type} & (IN): The type of the information to retrieve.\\
  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the connector.\\
  \texttt{arguments} & (IN/OUT): argument list containing parameters and
  output pointers for the get operation. \\
\end{tabular}
\end{mdframed}

@@

\item \texttt{H5VL\_ATTR\_GET\_INFO}, to retrieve the attribute info:
  \begin{enumerate}
  \item \texttt{H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
    explained in Section~\ref{sec:map}. 
  \item \texttt{H5A\_info\_t *ainfo} (OUT): info structure to fill the
    attribute info in.
  \end{enumerate}

\item \texttt{H5VL\_ATTR\_GET\_NAME}, to retrieve an attribute name on a
  particular object specified in \texttt{obj}:
  \begin{enumerate}
  \item \texttt{H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
    explained in Section~\ref{sec:map}. The type could be either
    \texttt{H5VL\_OBJECT\_BY\_SELF} meaning \texttt{obj} is the attribute,
    or \texttt{H5VL\_OBJECT\_BY\_IDX} meaning the attribute to retrieve
    the name for should be looked up using the index information on
    the object in \texttt{obj} and the index information in \texttt{loc\_params}.
  \item \texttt{size\_t buf\_size} (IN): the size of the buffer to store
    the name in.
  \item \texttt{void *buf} (OUT): Buffer to store the name in.
  \item \texttt{ssize\_t *ret\_val} (OUT): return the actual size needed
    to store the fill attribute name.
  \end{enumerate}

@@

\item \texttt{H5VL\_ATTR\_EXISTS}, to check if an attribute exists on a
  particular object specified in \texttt{obj}:
  \begin{enumerate}
  \item \texttt{H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
    explained in Section~\ref{sec:map}.
  \item \texttt{char *attr\_name} (IN): the attribute name to check.
  \item \texttt{htri\_t *ret} (OUT): existence result, 0 if false, 1 if true.
  \end{enumerate}

@@

\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
    herr_t (*write)(void *dset, hid_t mem_type_id, hid_t mem_space_id, 
        hid_t file_space_id, hid_t dxpl_id, const void * buf, void **req);
\end{lstlisting}

@@

\begin{itemize}
\item \texttt{H5VL\_OBJECT\_GET\_CONT\_INFO}, get the container that the object
  belongs to:
  \begin{enumerate}
  \item \texttt{H5I\_type\_t type} (IN): the object type in \texttt{obj}.
  \item \texttt{void **ret} (OUT): pointer to the file structure returned
    by the connector.
  \end{enumerate}

@@

\item \texttt{H5VL\_FILE\_GET\_FILENO}, to retrieve the file's file number:
  \begin{enumerate}
  \item \texttt{hid\_t *ret\_id} (OUT): buffer for the identifier of the
    file creation property list.
  \end{enumerate}

\item \texttt{H5VL\_FILE\_GET\_INTENT}, get access intent of the
  container:
  \begin{enumerate}
  \item \texttt{unsigned *ret} (OUT): buffer for the intent value.
  \end{enumerate}

@@

The \texttt{specific\_type} argument is an \texttt{enum}:
\begin{lstlisting}
/* types for file SPECIFIC callback */
typedef enum H5VL_file_specific_t {                                              
    H5VL_FILE_POST_OPEN,                    /* Adjust file after open, with wrapping context */
    H5VL_FILE_FLUSH,                        /* Flush file                       */
    H5VL_FILE_REOPEN,                       /* Reopen the file                  */
    H5VL_FILE_MOUNT,                        /* Mount a file                     */
    H5VL_FILE_UNMOUNT,                      /* Unmount a file                   */
    H5VL_FILE_IS_ACCESSIBLE,                /* Check if a file is accessible    */
    H5VL_FILE_DELETE                        /* Delete a file                    */
} H5VL_file_specific_t;
\end{lstlisting}

@@

\begin{itemize}
\item \texttt{H5VL\_FILE\_POST\_OPEN}, adjust a file after opening it:
  \begin{enumerate}
  \item \texttt{H5I\_type\_t obj\_type} (IN): The object type of \texttt{obj} on which the flush operation was called.
  \item \texttt{H5F\_scope\_t scope} (IN): The scope of the flushing action.
  \end{enumerate}

@@

\item \texttt{H5VL\_FILE\_REOPEN}, reopens a file:
  \begin{enumerate}
  \item \texttt{H5I\_type\_t obj\_type} (IN): The object type of \texttt{obj} on which the flush operation was called.
  \item \texttt{H5F\_scope\_t scope} (IN): The scope of the flushing action.
  \end{enumerate}

\item \texttt{H5VL\_FILE\_MOUNT}, Mounts a file on the location object:
  \begin{enumerate}
  \item \texttt{H5I\_type\_t type} (IN): the object type in \texttt{obj}.
  \item \texttt{char *name} (IN): name of the group onto which the file
    specified by \texttt{file} is to be mounted.
  \item \texttt{void *file} (IN): child file to be mounted.
  \item \texttt{hid\_t *fmpl\_id} (IN): file mount property list.
  \end{enumerate}

@@

\item \texttt{H5VL\_FILE\_DELETE}, deletes a file:
  \begin{enumerate}
  \item \texttt{H5I\_type\_t obj\_type} (IN): The object type of \texttt{obj} on which the flush operation was called.
  \item \texttt{H5F\_scope\_t scope} (IN): The scope of the flushing action.
  \end{enumerate}
 \end{itemize}
\end{mdframed}

@@

\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
    void *(*create)(void *obj, H5VL_loc_params_t loc_params, const char *name, hid_t gcpl_id, hid_t gapl_id, hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
  \texttt{obj} & (IN): Pointer to an object where the group needs
  to be created or where the look-up of the target object needs to
  start.\\
  \texttt{loc\_params} & (IN): The location parameters as explained in
  Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_SELF} in this callback. \\
  \texttt{name} & (IN): The name of the group to be created.\\
  \texttt{dcpl\_id} & (IN): The group creation property list. It contains
  all the group creation properties in addition to the link creation
  property list of the create operation (an \texttt{hid\_t}) that can be
  retrieved with the property \texttt{H5VL\_GRP\_LCPL\_ID}.\\
  \texttt{gapl\_id} & (IN): The group access property list.\\
  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the connector.\\
\end{tabular}
\end{mdframed}

@@

\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
    void *(*open)(void *obj, H5VL_loc_params_t loc_params, 
        const char*name, hid_t gapl_id, hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
  \texttt{obj} & (IN): Pointer to an object where the group needs to be
  opened or where the look-up of the target object needs to start.\\
  \texttt{loc\_params} & (IN): The location parameters as explained in
  Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_SELF} in this callback. \\
  \texttt{name} & (IN): The name of the group to be opened.\\
  \texttt{dapl\_id} & (IN): The group access property list.\\
  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the connector.\\
\end{tabular}
\end{mdframed}

@@

\item \texttt{H5VL\_GROUP\_GET\_INFO}, to retrieve the attribute info:
  \begin{enumerate}
  \item \texttt{H5VL\_loc\_params\_t loc\_params} (IN): The location parameters
    explained in Section~\ref{sec:map}. 
  \item \texttt{H5G\_info\_t *ginfo} (OUT): info structure to fill the
    group info in.
  \end{enumerate}
\end{itemize}

@@

\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
	herr_t (*specific)(void *obj, H5VL_loc_params_t loc_params, H5VL_object_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
\end{lstlisting}

@@

\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
  \texttt{obj} & (IN): The container or object where the operation needs to happen.\\
  \texttt{loc\_params} & (IN): The location parameters as explained in Section~\ref{sec:map}.\\
  \texttt{specific\_type} & (IN): The type of the operation.\\
  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the connector.\\
  \texttt{arguments} & (IN/OUT): argument list containing parameters and
  output pointers for the get operation. \\
\end{tabular}
\end{mdframed}

@@

\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
    herr_t (*create)(H5VL_link_create_type_t create_type, void *obj,
        H5VL_loc_params_t loc_params, hid_t lcpl_id, 
        hid_t lapl_id, hid_t dxpl_id, void **req);
\end{lstlisting}

@@

\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
  \texttt{create\_type} & (IN): type of the link to be created.\\
  \texttt{obj} & (IN): Pointer to an object where the link needs to be
  created from.\\
  \texttt{loc\_params} & (IN): The location parameters as explained in
  Section~\ref{sec:map} for the source object. \\
  \texttt{lcpl\_id} & (IN): The link creation property list. It contains
  all the link creation properties in addition to other API parameters
  depending on the creation type, which will be detailed next.\\
  \texttt{lapl\_id} & (IN): The link access property list.\\
  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the connector.\\
\end{tabular}
\end{mdframed}

@@

\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
    herr_t (*copy)(void *src_obj, H5VL_loc_params_t loc_params1, void *dst_obj, H5VL_loc_params_t loc_params2, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
  \texttt{src\_obj} & (IN): original/source object or file. \\
  \texttt{loc\_params1} & (IN): The location parameters for the source
  object as explained in Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_NAME} in this callback. \\
  \texttt{dst\_obj} & (IN): destination object or file. \\
  \texttt{loc\_params1} & (IN): The location parameters for the destination
  object as explained in Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_NAME} in this callback. \\
  \texttt{lcpl\_id} & (IN): The link creation property list.\\
  \texttt{lapl\_id} & (IN): The link access property list.\\
  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the connector.\\
\end{tabular}
\end{mdframed}

@@

\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
    herr_t (*move)(void *src_obj, H5VL_loc_params_t loc_params1, void *dst_obj, H5VL_loc_params_t loc_params2, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
  \texttt{src\_obj} & (IN): original/source object or file. \\
  \texttt{loc\_params1} & (IN): The location parameters for the source
  object as explained in Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_NAME} in this callback. \\
  \texttt{dst\_obj} & (IN): destination object or file. \\
  \texttt{loc\_params1} & (IN): The location parameters for the destination
  object as explained in Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_NAME} in this callback. \\
  \texttt{lcpl\_id} & (IN): The link creation property list.\\
  \texttt{lapl\_id} & (IN): The link access property list.\\
  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the connector.\\
\end{tabular}
\end{mdframed}

@@

\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
    herr_t (*get)(void *obj, H5VL_loc_params_t loc_params, 
        H5VL_link_get_t get_type, hid_t dxpl_id, void **req, 
        va_list arguments);
\end{lstlisting}

@@

\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
  \texttt{obj} & (IN): The file or group object where information needs to be
  retrieved from.\\
  \texttt{loc\_params} & (IN): The location parameters for the source
  object as explained in Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_NAME} or \texttt{H5VL\_OBJECT\_BY\_IDX} in this
  callback.\\ 
  \texttt{get\_type} & (IN): The type of the information to retrieve.\\
  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the connector.\\
  \texttt{arguments} & (IN/OUT): argument list containing parameters and
  output pointers for the get operation. \\
\end{tabular}
\end{mdframed}

@@

\begin{itemize}
\item \texttt{H5VL\_LINK\_GET\_INFO}, to retrieve the link info from the
  link specified in the \texttt{loc\_params}:
  \begin{enumerate}
  \item \texttt{H5L\_info\_t linfo} (OUT): pointer to info structure to
    fill.
  \end{enumerate}

@@

\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
	herr_t (*specific)(void *obj, H5VL_loc_params_t loc_params, H5VL_link_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
\end{lstlisting}

@@

\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
  \texttt{obj} & (IN): The location object  where the operation needs to happen.\\
  \texttt{loc\_params} & (IN): The location parameters as explained in Section~\ref{sec:map}.\\
  \texttt{specific\_type} & (IN): The type of the operation.\\
  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the connector.\\
  \texttt{arguments} & (IN/OUT): argument list containing parameters and
  output pointers for the get operation. \\
\end{tabular}
\end{mdframed}

@@

\item \texttt{H5VL\_LINK\_EXITS}, to determine whether the link specified
  in the \texttt{loc\_params} exits (\texttt{loc\_params} is of type \texttt{H5VL\_OBJECT\_BY\_NAME} only with this type):
  \begin{enumerate}
  \item \texttt{htri\_t *ret} (OUT): buffer for the existence of the link
    (0 for no, 1 for yes).
  \end{enumerate}

\item \texttt{H5VL\_LINK\_ITER}, to iterate over all links starting at the location provided and call a user-specified callback on each one:
  \begin{enumerate}
  \item \texttt{hbool\_t recursive} (IN): whether to recursively follow links into subgroups of the specified group.\\
  \item \texttt{H5\_index\_t idx\_type} (IN): Type of index.\\
  \item \texttt{H5\_iter\_order\_t order} (IN): Order in which to iterate over index.\\
  \item \texttt{hsize\_t *idx} (IN/OUT):  iteration position where to start and return position where an interrupted iteration may restart.\\
  \item \texttt{H5L\_iterate\_t op} (IN): User-defined function to pass each link to. \\
  \item \texttt{void *op\_data} (IN/OUT): User data to pass through to and to be returned by iterator operator function. \\
  \end{enumerate}
\end{itemize}

@@

The \texttt{get\_type} argument is an \texttt{enum}:
\begin{lstlisting}
/* type for object GET callback */
typedef enum H5VL_object_get_t {                                                 
    H5VL_OBJECT_GET_NAME,              /* object name                       */   
    H5VL_OBJECT_GET_TYPE               /* object type                       */   
} H5VL_object_get_t; 
\end{lstlisting}

@@

\begin{itemize}
\item \texttt{H5VL\_OBJECT\_GET\_NAME}, to retrieve a name for a referenced object:
  \begin{enumerate}
  \item \texttt{ssize\_t *ret} (OUT): buffer to return the length of the
    name.
  \item \texttt{char* name} (OUT): buffer to copy the name into.
  \item \texttt{size\_t size} (IN): size of the buffer name, if 0, return
    only the buffer size needed.
  \item \texttt{H5R\_type\_t ret\_type} (IN): type of region reference to
    query.
  \item \texttt{void *ref} (IN): the region reference to query.
  \end{enumerate}

>>>>

\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
  \texttt{obj} & (IN): An attribute or location object where information
  needs to be retrieved from.\\
  \texttt{get\_type} & (IN): The type of the information to retrieve.\\
  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the connector.\\
  \texttt{arguments} & (IN/OUT): argument list containing parameters and
  output pointers for the get operation. \\
\end{tabular}
\end{mdframed}

@@

\item \texttt{H5VL\_ATTR\_GET\_INFO}, to retrieve the attribute info:
  \begin{enumerate}
  \item \texttt{H5VL\_loc\_params\_t *loc\_params} (IN): Pointer to the location parameters
    explained in Section~\ref{sec:map}. 
  \item \texttt{H5A\_info\_t *ainfo} (OUT): info structure to fill the
    attribute info in.
  \end{enumerate}

\item \texttt{H5VL\_ATTR\_GET\_NAME}, to retrieve an attribute name on a
  particular object specified in \texttt{obj}:
  \begin{enumerate}
  \item \texttt{H5VL\_loc\_params\_t *loc\_params} (IN): Pointer to the location parameters
    explained in Section~\ref{sec:map}. The type could be either
    \texttt{H5VL\_OBJECT\_BY\_SELF} meaning \texttt{obj} is the attribute,
    or \texttt{H5VL\_OBJECT\_BY\_IDX} meaning the attribute to retrieve
    the name for should be looked up using the index information on
    the object in \texttt{obj} and the index information in \texttt{loc\_params}.
  \item \texttt{size\_t buf\_size} (IN): the size of the buffer to store
    the name in.
  \item \texttt{void *buf} (OUT): Buffer to store the name in.
  \item \texttt{ssize\_t *ret\_val} (OUT): return the actual size needed
    to store the fill attribute name.
  \end{enumerate}

@@

\item \texttt{H5VL\_ATTR\_EXISTS}, to check if an attribute exists on a
  particular object specified in \texttt{obj}:
  \begin{enumerate}
  \item \texttt{char *attr\_name} (IN): the attribute name to check.
  \item \texttt{htri\_t *ret} (OUT): existence result, 0 if false, 1 if true.
  \end{enumerate}

@@

\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
    herr_t (*write)(void *dset, hid_t mem_type_id, hid_t mem_space_id, 
        hid_t file_space_id, hid_t dxpl_id, const void *buf, void **req);
\end{lstlisting}

@@

\begin{itemize}
\item \texttt{H5VL\_OBJECT\_GET\_CONT\_INFO}, get information about the container
    that the object belongs to:
  \begin{enumerate}
  \item \texttt{H5VL\_file\_cont\_info\_t *info} (OUT): pointer to the file
    container info structure returned.
  \end{enumerate}

@@

\item \texttt{H5VL\_FILE\_GET\_FILENO}, to retrieve the file's file number:
  \begin{enumerate}
  \item \texttt{unsigned long *fileno} (OUT): buffer for the file number.
  \end{enumerate}

\item \texttt{H5VL\_FILE\_GET\_INTENT}, get access intent of the
  container:
  \begin{enumerate}
  \item \texttt{unsigned *intent\_flags} (OUT): buffer for the intent flags value.
  \end{enumerate}

@@

The \texttt{specific\_type} argument is an \texttt{enum}:
\begin{lstlisting}
/* types for file SPECIFIC callback */
typedef enum H5VL_file_specific_t {                                              
    H5VL_FILE_POST_OPEN,                    /* Adjust file after open, with wrapping context */
    H5VL_FILE_FLUSH,                        /* Flush file                       */
    H5VL_FILE_REOPEN,                       /* Reopen the file                  */
    H5VL_FILE_MOUNT,                        /* Mount a file                     */
    H5VL_FILE_UNMOUNT,                      /* Unmount a file                   */
    H5VL_FILE_IS_ACCESSIBLE,                /* Check if a file is accessible    */
    H5VL_FILE_DELETE,                       /* Delete a file                    */
    H5VL_FILE_IS_EQUAL                      /* Check if two files are the same  */
} H5VL_file_specific_t;
\end{lstlisting}

@@

\begin{itemize}
\item \texttt{H5VL\_FILE\_POST\_OPEN}, adjust a file after opening it:

@@

\item \texttt{H5VL\_FILE\_REOPEN}, reopens a file:
  \begin{enumerate}
      \item \texttt{void *file} (IN): pointer to the reopened file (same type
          of pointer as is returned from the connector's create/open callbacks).
  \end{enumerate}

\item \texttt{H5VL\_FILE\_MOUNT}, Mounts a file on the location object:
  \begin{enumerate}
  \item \texttt{H5I\_type\_t type} (IN): the object type in \texttt{obj}.
  \item \texttt{char *name} (IN): name of the group onto which the file
    specified by \texttt{file} is to be mounted.
  \item \texttt{void *child} (IN): child file to be mounted (same type
          of pointer as is returned from the connector's create/open callbacks).
  \item \texttt{hid\_t *fmpl\_id} (IN): file mount property list.
  \end{enumerate}

@@

\item \texttt{H5VL\_FILE\_DELETE}, deletes a file:
  \begin{enumerate}
  \item \texttt{H5I\_type\_t obj\_type} (IN): The object type of \texttt{obj} on which the flush operation was called.
  \item \texttt{H5F\_scope\_t scope} (IN): The scope of the flushing action.
  \end{enumerate}

\item \texttt{H5VL\_FILE\_IS\_EQUAL}, check if one file is equal to another:
  \begin{enumerate}
  \item \texttt{H5I\_type\_t obj\_type} (IN): The object type of \texttt{obj} on which the flush operation was called.
  \item \texttt{H5F\_scope\_t scope} (IN): The scope of the flushing action.
  \end{enumerate}

@@

\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
    void *(*create)(void *obj, H5VL_loc_params_t *loc_params, const char *name, hid_t gcpl_id, hid_t gapl_id, hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
  \texttt{obj} & (IN): Pointer to an object where the group needs
  to be created or where the look-up of the target object needs to
  start.\\
  \texttt{loc\_params} & (IN): Pointer to the location parameters as explained in
  Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_SELF} in this callback. \\
  \texttt{name} & (IN): The name of the group to be created.\\
  \texttt{dcpl\_id} & (IN): The group creation property list. It contains
  all the group creation properties in addition to the link creation
  property list of the create operation (an \texttt{hid\_t}) that can be
  retrieved with the property \texttt{H5VL\_GRP\_LCPL\_ID}.\\
  \texttt{gapl\_id} & (IN): The group access property list.\\
  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the connector.\\
\end{tabular}
\end{mdframed}

@@

\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
    void *(*open)(void *obj, H5VL_loc_params_t *loc_params, 
        const char*name, hid_t gapl_id, hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
  \texttt{obj} & (IN): Pointer to an object where the group needs to be
  opened or where the look-up of the target object needs to start.\\
  \texttt{loc\_params} & (IN): Pointer to the location parameters as explained in
  Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_SELF} in this callback. \\
  \texttt{name} & (IN): The name of the group to be opened.\\
  \texttt{dapl\_id} & (IN): The group access property list.\\
  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the connector.\\
\end{tabular}
\end{mdframed}

@@

\item \texttt{H5VL\_GROUP\_GET\_INFO}, to retrieve the attribute info:
  \begin{enumerate}
  \item \texttt{H5VL\_loc\_params\_t *loc\_params} (IN): Pointer to the location
      parameters explained in Section~\ref{sec:map}. 
  \item \texttt{H5G\_info\_t *group\_info} (OUT): info structure to fill the
    group info in.
  \end{enumerate}
\end{itemize}

@@

@@

\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
  \texttt{obj} & (IN): The container or object where the operation needs to happen.\\
  \texttt{loc\_params} & (IN): Pointer to the location parameters as explained in Section~\ref{sec:map}.\\
  \texttt{specific\_type} & (IN): The type of the operation.\\
  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the connector.\\
  \texttt{arguments} & (IN/OUT): argument list containing parameters and
  output pointers for the get operation. \\
\end{tabular}
\end{mdframed}

@@

\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
    herr_t (*create)(H5VL_link_create_type_t create_type, void *obj,
        H5VL_loc_params_t *loc_params, hid_t lcpl_id, 
        hid_t lapl_id, hid_t dxpl_id, void **req);
\end{lstlisting}

@@

\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
  \texttt{create\_type} & (IN): type of the link to be created.\\
  \texttt{obj} & (IN): Pointer to an object where the link needs to be
  created from.\\
  \texttt{loc\_params} & (IN): Pointer to the location parameters as explained in
  Section~\ref{sec:map} for the source object. \\
  \texttt{lcpl\_id} & (IN): The link creation property list. It contains
  all the link creation properties in addition to other API parameters
  depending on the creation type, which will be detailed next.\\
  \texttt{lapl\_id} & (IN): The link access property list.\\
  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the connector.\\
\end{tabular}
\end{mdframed}

@@

\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
    herr_t (*copy)(void *src_obj, H5VL_loc_params_t *loc_params1, void *dst_obj, H5VL_loc_params_t *loc_params2, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
  \texttt{src\_obj} & (IN): original/source object or file. \\
  \texttt{loc\_params1} & (IN): Pointer to the location parameters for the source
  object as explained in Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_NAME} in this callback. \\
  \texttt{dst\_obj} & (IN): destination object or file. \\
  \texttt{loc\_params1} & (IN): Pointer to the location parameters for the destination
  object as explained in Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_NAME} in this callback. \\
  \texttt{lcpl\_id} & (IN): The link creation property list.\\
  \texttt{lapl\_id} & (IN): The link access property list.\\
  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the connector.\\
\end{tabular}
\end{mdframed}

@@

\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
    herr_t (*move)(void *src_obj, H5VL_loc_params_t *loc_params1, void *dst_obj, H5VL_loc_params_t *loc_params2, hid_t lcpl_id, hid_t lapl_id, hid_t dxpl_id, void **req);
\end{lstlisting}

\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
  \texttt{src\_obj} & (IN): original/source object or file. \\
  \texttt{loc\_params1} & (IN): Pointer to the location parameters for the source
  object as explained in Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_NAME} in this callback. \\
  \texttt{dst\_obj} & (IN): destination object or file. \\
  \texttt{loc\_params1} & (IN): Pointer to the location parameters for the destination
  object as explained in Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_NAME} in this callback. \\
  \texttt{lcpl\_id} & (IN): The link creation property list.\\
  \texttt{lapl\_id} & (IN): The link access property list.\\
  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the connector.\\
\end{tabular}
\end{mdframed}

@@

\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
    herr_t (*get)(void *obj, H5VL_loc_params_t *loc_params, 
        H5VL_link_get_t get_type, hid_t dxpl_id, void **req, 
        va_list arguments);
\end{lstlisting}

@@

\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
  \texttt{obj} & (IN): The file or group object where information needs to be
  retrieved from.\\
  \texttt{loc\_params} & (IN): Pointer to the location parameters for the source
  object as explained in Section~\ref{sec:map}. The type can be only \texttt{H5VL\_OBJECT\_BY\_NAME} or \texttt{H5VL\_OBJECT\_BY\_IDX} in this
  callback.\\ 
  \texttt{get\_type} & (IN): The type of the information to retrieve.\\
  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the connector.\\
  \texttt{arguments} & (IN/OUT): argument list containing parameters and
  output pointers for the get operation. \\
\end{tabular}
\end{mdframed}

@@

\begin{itemize}
\item \texttt{H5VL\_LINK\_GET\_INFO}, to retrieve the link info from the
  link specified in the \texttt{loc\_params}:
  \begin{enumerate}
  \item \texttt{H5L\_info\_t *linfo} (OUT): pointer to info structure to
    fill.
  \end{enumerate}

@@

\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
	herr_t (*specific)(void *obj, H5VL_loc_params_t *loc_params, H5VL_link_specific_t specific_type, hid_t dxpl_id, void **req, va_list arguments);
\end{lstlisting}

@@

\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
  \texttt{obj} & (IN): The location object  where the operation needs to happen.\\
  \texttt{loc\_params} & (IN): Pointer to the location parameters as explained in Section~\ref{sec:map}.\\
  \texttt{specific\_type} & (IN): The type of the operation.\\
  \texttt{dxpl\_id} & (IN): The data transfer property list.\\
  \texttt{req} & (IN/OUT): A pointer to the asynchronous request of the
  operation created by the connector.\\
  \texttt{arguments} & (IN/OUT): argument list containing parameters and
  output pointers for the get operation. \\
\end{tabular}
\end{mdframed}

@@

\item \texttt{H5VL\_LINK\_EXISTS}, to determine whether the link specified
  in the \texttt{loc\_params} exits (\texttt{loc\_params} is of type \texttt{H5VL\_OBJECT\_BY\_NAME} only with this type):
  \begin{enumerate}
  \item \texttt{htri\_t *ret} (OUT): buffer for the existence of the link
    (0 for no, 1 for yes).
  \end{enumerate}

\item \texttt{H5VL\_LINK\_ITER}, to iterate over all links starting at the location provided and call a user-specified callback on each one:
  \begin{enumerate}
  \item \texttt{hbool\_t recursive} (IN): whether to recursively follow links into subgroups of the specified group.\\
  \item \texttt{H5\_index\_t idx\_type} (IN): Type of index.\\
  \item \texttt{H5\_iter\_order\_t order} (IN): Order in which to iterate over index.\\
  \item \texttt{hsize\_t *idx\_p} (IN/OUT):  iteration position where to start and return position where an interrupted iteration may restart.\\
  \item \texttt{H5L\_iterate\_t op} (IN): User-defined function to pass each link to. \\
  \item \texttt{void *op\_data} (IN/OUT): User data to pass through to and to be returned by iterator operator function. \\
  \end{enumerate}
\end{itemize}

@@

The \texttt{get\_type} argument is an \texttt{enum}:
\begin{lstlisting}
/* type for object GET callback */
typedef enum H5VL_object_get_t {                                                 
    H5VL_OBJECT_GET_FILE,              /* object's file                     */   
    H5VL_OBJECT_GET_NAME,              /* object name                       */   
    H5VL_OBJECT_GET_TYPE               /* object type                       */   
} H5VL_object_get_t; 
\end{lstlisting}

@@

\begin{itemize}
\item \texttt{H5VL\_OBJECT\_GET\_FILE}, to retrieve a file for a referenced object:
  \begin{enumerate}
  \item \texttt{void **ret} (OUT): pointer to buffer to return the file.
  \end{enumerate}

 \item \texttt{H5VL\_OBJECT\_GET\_NAME}, to retrieve a name for a referenced object:
  \begin{enumerate}
  \item \texttt{ssize\_t *ret} (OUT): buffer to return the length of the
    name.
  \item \texttt{char* name} (OUT): buffer to copy the name into.
  \item \texttt{size\_t size} (IN): size of the buffer name, if 0, return
    only the buffer size needed.
  \end{enumerate}
